\documentclass{beamer}
\usepackage{amsmath}
\setbeameroption{show notes on second screen=right}
\setbeamertemplate{note page}[plain]
\setbeamerfont{note page}{size=\footnotesize}
\beamertemplatenavigationsymbolsempty

\begin{document}

\begin{frame}
\frametitle{}

Which of these equations is the equation of the line going through $(2,0)$ and $(0,4)$?
\begin{enumerate}[a]
    \item $x+2y=4$
    \item $2x+y=4$
    \item $-2x+y=4$
    \item $2x-y=4$
    \item $x-2y=4$
\end{enumerate}

\note{\alert<1>{Which of these equations is the equation of the line going through (2,0) and (0,4)? A, x + 2y = 4. B, 2x + y = 4. C, -2x + y = 4. D, 2x - y = 4. E, x - 2y = 4.}}

\pause\note{\alert<2>{We can check which equation is correct by plugging in the coordinates of the two points. That is, both points need to satisfy the equation that is relevant.}}
\pause
\vskip4pt
\hrule
\vskip4pt
$x+2y=4$\note{\alert<3>{Let's check the first equation x plus 2y equals 4 with the points (2,0) and (0,4).}}
\vskip4pt
\pause $2+2(0)=4$\note{\alert<4>{Plugging in the point (2,0) into the equation x + 2y = 4, we get 2 + 2(0) = 4, which is false since the left side simplifies to 2 and the right side simplifies to 4. We don't bother checking the other point.}}

\pause 
\vskip4pt
\hrule
\vskip4pt
$2x+y=4$\note{\alert<5>{Let's check the second equation 2x plus y equals 4 with the points (2,0) and (0,4).}}
\vskip4pt
\pause $2(2)+0=4$\note{\alert<6>{Plugging in the point (2,0) into the equation 2x + y = 4, we get 2(2) + 0 = 4, which is true, since both sides simplify to 4.}}
\vskip4pt
\pause $2(0)+4=4$\note{\alert<7>{Plugging in the point (0,4) into the equation 2x + y = 4, we get 2(0) + 4 = 4, which is true, since both sides simplify to 4.}}
\vskip4pt

\pause $2x+y=4$ is the equation going through $(2,0)$ and $(0,4)$.
\note{\alert<8>{So, equation B, which is 2 x plus y equals 4, is the correct equation. This equation goes through both the point (2,0) and the point (0,4).}}


\end{frame}



%% Blank frames at the end to prevent weird shifts.
\begin{frame}
\end{frame}
\begin{frame}
\end{frame}
\begin{frame}
\end{frame}
\begin{frame}
\end{frame}
\begin{frame}
\end{frame}
\begin{frame}
\end{frame}

\end{document}
